Self Regulation Ontology Retest Analyses

### 2018-07-27 code/SRO_Retest_Analyses.Rmd
removed model files from git repo

# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds')
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds')
summary(m)
```

```{r}
# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds')
summary(m)
```

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
summary(MCMCglmm(icc ~ num_all_trials, random=~dv, data = tmp))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
```

>>>>

# summary(lmerTest::lmer(var_subs_pct~task+(1|dv),tmp%>%select(-var_ind_pct,-var_resid_pct)))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_subs_pct_by_task_model.rds.gz'))
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(var_ind_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_resid_pct)))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_ind_pct_by_task_model.rds.gz'))
summary(m)
```

```{r}
# summary(lmerTest::lmer(var_resid_pct~task+(1|dv),tmp%>%select(-var_subs_pct,-var_ind_pct)))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/var_resid_pct_by_task_model.rds'))
summary(m)
```

@@

# summary(lm(icc ~ num_all_trials, data = tmp))
# summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_num_trials_model.rds'))
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp))
```

@@

```{r}
# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds.gz'))
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
m = readRDS(gzfile('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds.gz'))
summary(m)
```
